Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-04 paper/paper-nature-revised.tex
add csl to correct reference style

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 3, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many other Commonwealth countries, such as
Canada and Australia (Vice and Farrell 2017). Given the content and
magnitude of these records, they have significance, particularly in the
context of political science research. In the case of Canada, the
Hansard has been digitized for 1901 to 2019 (Beelen et al. 2017). Having
a digitized version of Hansard enables researchers to conduct text
analysis and statistical modelling. Following the lead of that project,
in this paper we introduce a similar database for Australia. This is
composed of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form that can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a resource for understanding political behaviour in
Australia over time.

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1).
Politicians in the House are referred to as Members of Parliament (MPs).
The House operates under a parallel chamber setup, meaning there are two
debate venues where proceedings take place: the Chamber, and the
Federation Chamber. Sittings of the House follow a predefined order of
business, regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of these proceedings on which Hansard is based, and it is
essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance, Sherratt (2016) created an online, easy to read
database of Hansard from 1901 to 1980 using the XML files. These data
can be navigated by year, parliament, people, and bills (Sherratt 2016).
To make the Australian Parliamentary Handbook more accessible, Leslie
(2021) has released an \texttt{R} package which includes data on all MPs
from 1945 to 2019. Further, Alexander and Hodgetts (2021) created the
\texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used the Hansard
to investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark. Rasiah (2010) worked
with Question Time data from Hansard transcripts during February and
March of 2003, to investigate resistance of politicians in answering
questions about Iraq. Fraussen, Graham, and Halpin (2018) use Hansard to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials. Finally, Alexander and Alexander
(2021) construct a dataset of the Australian Hansard, along with an
analysis of the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament. Alexander and Alexander (2021) created
this database with the static PDF versions of Hansard, using OCR to
digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages (Temple Lang 2022; Wickham, Hester, and Ooms 2021). Focusing on
one transcript also allowed us to ensure that all key components of the
transcript were parsed and captured in as much detail as possible. The
typical form of a Hansard XML transcript is summarized in the nested
list below. This provides an overview, but does not contain every
possible nested element that may be found in a Hansard XML.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by Wickham (2014). These contain all
parsed text elements, where each statement is separated onto its own row
with details about the MP who is speaking, and rows are maintained in
chronological order. This first involved correcting the variable classes
and adding several indicator variables to differentiate where statements
came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in mid-2012
(House of Representatives 2018, ch.~21). As a result, the child node
under which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real time (House of
Representatives 2021). Questions without notice are included directly in
the \texttt{"chamber.xscript"} child node, with sub-child nodes called
\texttt{"question"} and \texttt{"answer"} to differentiate the two.
Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table (Alexander and Hodgetts 2021).

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022 \textbf{where an XML transcript is available}, so there
are \textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 (Katz and
Alexander 2023). For each \textbf{Hansard data} file, \textbf{that is,
the corpus and the individual sitting day files}, each row contains an
individual statement, with details on the individual speaking. For
general statements transcribed as made by ``Honourable members'' for
example, these variables cannot be specified. Table~\ref{tbl-vars}
provides an overview of each variable found in the \textbf{Hansard data
files in the} database.

@@

\textbf{Next, we explored the number of unique names detected on each
sitting day disaggregated by debate venue, visualized in
Figure~\ref{fig-names}. As expected, there are generally more individual
MPs detected to be present in the Chamber proceedings in our data than
in the Federation Chamber proceedings. Further, in both venues, the
number of individuals detected per sitting day appears to have increased
since around 2008-2009, with a maximum of 116 and 87 unique names
detected for the Chamber and Federation Chamber, respectively. Across
the time frame of our data, there was a daily average of 84 unique names
detected in the Chamber, and 34 in the Federation Chamber. These
observations are in accordance with the official number of Members
belonging to the House of Representatives, which was 148 in 1998, 150 in
2001, and then increased to 151 in the 2019 general election (House of
Representatives 2018).}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives (Parliament of Australia 2022).}

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
Alexander 2019). By including this variable, one can readily integrate
our data records with those available in these two packages.
\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
data which allows users to link our data to external political party
data sources with this unique identifier.}

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook (Leslie 2021). This will allow for
convenient extraction of further details on each MP in a tidy, ready to
analyze format.

@@

The code written to build this database is available on the GitHub
repository associated with this paper:
https://github.com/lindsaykatz/hansard-proj. All scripts were created
using R software (R Core Team 2022). The core packages used to develop
these scripts are: the \texttt{XML} package by Temple Lang (2022), the
\texttt{xml2} package by Wickham, Hester, and Ooms (2021), the
\texttt{tidyverse} R packages by Wickham et al. (2019), the
\texttt{AustralianPoliticians} package by Alexander and Hodgetts (2021),
and the \texttt{ausPH} package by Leslie (2021). \texttt{XML} and
\texttt{xml2} were used for parsing the XML documents,
\texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
up and filling in MP details in the datasets, and \texttt{tidyverse}
packages were used in all steps, for tidy wrangling of data.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
Alexander, Rohan. 2019. \emph{AustralianElections: Datasets on
Australian Elections}.
\url{https://github.com/RohanAlexander/AustralianElections}.

\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
Alexander, Rohan, and Monica Alexander. 2021. {``The Increased Effect of
Elections and Changing Prime Ministers on Topics Discussed in the
Australian Federal Parliament Between 1901 and 2018.''} \emph{arXiv
Preprint arXiv:2111.09299}.

\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
Alexander, Rohan, and Paul A. Hodgetts. 2021.
\emph{AustralianPoliticians: Provides Datasets about Australian
Politicians}.
\url{https://CRAN.R-project.org/package=AustralianPoliticians}.

\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
Beelen, Kaspar, Timothy Alberdingk Thijm, Christopher Cochrane, Kees
Halvemaan, Graeme Hirst, Michael Kimmins, Sander Lijbrink, et al. 2017.
{``Digitization of the Canadian Parliamentary Debates.''} \emph{Canadian
Journal of Political Science/Revue Canadienne de Science Politique} 50
(3): 849--64.

\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
Fraussen, Bert, Timothy Graham, and Darren R Halpin. 2018. {``Assessing
the Prominence of Interest Groups in Parliament: A Supervised Machine
Learning Approach.''} \emph{The Journal of Legislative Studies} 24 (4):
450--74.

\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
House of Representatives. 2018. Edited by D. R. Elder and P. E. Fowler.
\emph{{House of Representatives Practice}}. 7th ed. {Australian
Government - Department of the House of Representatives}.

\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
---------. 2021. \emph{{A window on the house: Practices and procedures
relating to question time}}. {Parliament of Australia}.

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
database of all proceedings of the Australian Parliamentary Debates
(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7799678}.

\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
Leslie, Patrick. 2021. \emph{Members of the Australian House of
Representatives (1945-2019)}.
\url{https://github.com/palesl/AustralianHouseOfRepresentatives}.

\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
Parliament of Australia. 2022. {``Infosheet 22 - Political Parties.''}
\emph{House of Representatives Infosheets}.
\url{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}.

\leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
R Core Team. 2022. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
Rasiah, Parameswary. 2010. {``A Framework for the Systematic Analysis of
Evasion in Parliamentary Discourse.''} \emph{Journal of Pragmatics} 42
(3): 664--80.

\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
Salisbury, Christopher. 2011. {``'Mr Speaker, i Withdraw...': Standards
of (Mis) Behaviour in the Queensland, Western Australian and
Commonwealth Parliaments Compared via Online Hansard.''}
\emph{Australasian Parliamentary Review} 26 (1): 166--77.

\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
Sherratt, Tim. 2016. {``Documentation: Historic Hansard.''}
\emph{Historic Hansard}.
\url{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}.

\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
Temple Lang, Duncan. 2022. \emph{XML: Tools for Parsing and Generating
XML Within r and s-Plus}. \url{https://CRAN.R-project.org/package=XML}.

\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
Vice, John, and Stephen Farrell. 2017. \emph{The History of Hansard}.
House of Lords Library; House of Lords Hansard.

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical
Software} 59 (10). \url{https://doi.org/10.18637/jss.v059.i10}.

\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 4, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many other Commonwealth countries, such as
Canada and Australia\textsuperscript{1}. Given the content and magnitude
of these records, they have significance, particularly in the context of
political science research. In the case of Canada, the Hansard has been
digitized for 1901 to 2019\textsuperscript{2}. Having a digitized
version of Hansard enables researchers to conduct text analysis and
statistical modelling. Following the lead of that project, in this paper
we introduce a similar database for Australia. This is composed of
individual datasets for each sitting day in the House of Representatives
from 1998 to 2022, containing details on everything said in parliament
in a form that can be readily used by researchers. With the development
of tools for large-scale text analysis, this database will serve as a
resource for understanding political behaviour in Australia over time.

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure\textsuperscript{3, ch.~1}. Politicians in the
House are referred to as Members of Parliament (MPs). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders\textsuperscript{3, ch.~8}. A
typical sitting day in the Chamber has a number of scheduled proceedings
including debates on government business, 90 second member statements,
and Question Time\textsuperscript{3, ch.~8}. The Federation Chamber was
created in 1994 as a subordinate debate venue of the Chamber. This
allows for better time management of House business as its proceedings
occur simultaneously with those of the Chamber\textsuperscript{3,
ch.~21}. Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members\textsuperscript{3, ch.~21}. It is the recording and compilation
of these proceedings on which Hansard is based, and it is essentially,
but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance,\textsuperscript{4} created an online, easy to
read database of Hansard from 1901 to 1980 using the XML files. These
data can be navigated by year, parliament, people, and
bills\textsuperscript{4}. To make the Australian Parliamentary Handbook
more accessible,\textsuperscript{5} has released an \texttt{R} package
which includes data on all MPs from 1945 to 2019.
Further,\textsuperscript{6} created the \texttt{AustralianPoliticians}
\texttt{R} package, which contains several datasets related to the
political and biographical information of Australian federal politicians
who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example,\textsuperscript{7} used the
Hansard to investigate occurrences of unparliamentary comments by MPs,
where the Speaker tells that MP to withdraw their
remark.\textsuperscript{8} worked with Question Time data from Hansard
transcripts during February and March of 2003, to investigate resistance
of politicians in answering questions about Iraq.\textsuperscript{9} use
Hansard to quantify political prominence by investigating strategic
mentions of interest groups by elected officials.
Finally,\textsuperscript{10} construct a dataset of the Australian
Hansard, along with an analysis of the effect of elections and changes
in Prime Ministers upon topics mentioned in
parliament.\textsuperscript{10} created this database with the static
PDF versions of Hansard, using OCR to digitize these files into text
which is suitable for analysis. This means there are considerable
digitization errors especially in the first half of the dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages\textsuperscript{11,12}. Focusing on one transcript also allowed
us to ensure that all key components of the transcript were parsed and
captured in as much detail as possible. The typical form of a Hansard
XML transcript is summarized in the nested list below. This provides an
overview, but does not contain every possible nested element that may be
found in a Hansard XML.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{13}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{3, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{14}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table\textsuperscript{6}.

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022 \textbf{where an XML transcript is available}, so there
are \textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678\textsuperscript{15}. For each
\textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

\textbf{Next, we explored the number of unique names detected on each
sitting day disaggregated by debate venue, visualized in
Figure~\ref{fig-names}. As expected, there are generally more individual
MPs detected to be present in the Chamber proceedings in our data than
in the Federation Chamber proceedings. Further, in both venues, the
number of individuals detected per sitting day appears to have increased
since around 2008-2009, with a maximum of 116 and 87 unique names
detected for the Chamber and Federation Chamber, respectively. Across
the time frame of our data, there was a daily average of 84 unique names
detected in the Chamber, and 34 in the Federation Chamber. These
observations are in accordance with the official number of Members
belonging to the House of Representatives, which was 148 in 1998, 150 in
2001, and then increased to 151 in the 2019 general
election\textsuperscript{3}.}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives\textsuperscript{16}.}

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages\textsuperscript{6,17}. By
including this variable, one can readily integrate our data records with
those available in these two packages. \textbf{Similarly, we added the
\texttt{partyfacts\_id} variable to our data which allows users to link
our data to external political party data sources with this unique
identifier.}

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook\textsuperscript{5}. This will allow
for convenient extraction of further details on each MP in a tidy, ready
to analyze format.

@@

The code written to build this database is available on the GitHub
repository associated with this paper:
https://github.com/lindsaykatz/hansard-proj. All scripts were created
using R software\textsuperscript{18}. The core packages used to develop
these scripts are: the \texttt{XML} package by\textsuperscript{11}, the
\texttt{xml2} package by\textsuperscript{12}, the \texttt{tidyverse} R
packages by\textsuperscript{19}, the \texttt{AustralianPoliticians}
package by\textsuperscript{6}, and the \texttt{ausPH} package
by\textsuperscript{5}. \texttt{XML} and \texttt{xml2} were used for
parsing the XML documents, \texttt{AustralianPoliticians} and
\texttt{ausPH} were used for cleaning up and filling in MP details in
the datasets, and \texttt{tidyverse} packages were used in all steps,
for tidy wrangling of data.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Vice, J. \& Farrell, S. \emph{The history of hansard}.
(House of Lords Library; House of Lords Hansard, 2017).}

\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Beelen, K. \emph{et al.} Digitization of the canadian
parliamentary debates. \emph{Canadian Journal of Political Science/Revue
canadienne de science politique} \textbf{50}, 849--864 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{House of Representatives. \emph{{House of
Representatives Practice}} ({Australian Government - Department of the
House of Representatives}, 2018).}

\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Sherratt, T.
\href{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}{Documentation:
Historic hansard}. \emph{Historic Hansard} (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Leslie, P.
\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
of the australian house of representatives (1945-2019)}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Alexander, R. \& Hodgetts, P. A.
\emph{\href{https://CRAN.R-project.org/package=AustralianPoliticians}{AustralianPoliticians:
Provides datasets about australian politicians}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Salisbury, C. 'Mr speaker, i withdraw...': Standards of
(mis) behaviour in the queensland, western australian and commonwealth
parliaments compared via online hansard. \emph{Australasian
Parliamentary Review} \textbf{26}, 166--177 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Rasiah, P. A framework for the systematic analysis of
evasion in parliamentary discourse. \emph{Journal of Pragmatics}
\textbf{42}, 664--680 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Fraussen, B., Graham, T. \& Halpin, D. R. Assessing the
prominence of interest groups in parliament: A supervised machine
learning approach. \emph{The Journal of Legislative Studies}
\textbf{24}, 450--474 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Alexander, R. \& Alexander, M. The increased effect of
elections and changing prime ministers on topics discussed in the
australian federal parliament between 1901 and 2018. \emph{arXiv
preprint arXiv:2111.09299} (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Temple Lang, D.
\emph{\href{https://CRAN.R-project.org/package=XML}{XML: Tools for
parsing and generating XML within r and s-plus}}. (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Wickham, H., Hester, J. \& Ooms, J.
\emph{\href{https://CRAN.R-project.org/package=xml2}{xml2: Parse XML}}.
(2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Wickham, H.
\href{https://doi.org/10.18637/jss.v059.i10}{Tidy data}. \emph{Journal
of Statistical Software} \textbf{59}, (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{House of Representatives. \emph{{A window on the house:
Practices and procedures relating to question time}}. ({Parliament of
Australia}, 2021).}

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
of all proceedings of the Australian Parliamentary Debates (1998-2022)}.
(2023)
doi:\href{https://doi.org/10.5281/zenodo.7799678}{10.5281/zenodo.7799678}.}

\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Parliament of Australia.
\href{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}{Infosheet
22 - political parties}. \emph{House of Representatives Infosheets}
(2022).}

\leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Alexander, R.
\emph{\href{https://github.com/RohanAlexander/AustralianElections}{AustralianElections:
Datasets on australian elections}}. (2019).}
